The pollination trade-off

### 2018-03-01 publication/manuscript.Rmd
Figure with model predictions

@@

@@

## Awknoledgements

>>>>

```{r fig-trade-off-predictions, fig.width=3.5, fig.height= 2.5, fig.cap = "Trade off predictions"}
loadd(trade_off_predictions)

trade_off_predictions %>%
  mutate_at(c("conspecific", "heterospecific"), exp) %>%
  mutate(gain = conspecific / (conspecific + heterospecific)) %>%
  filter(!(value > 2.2 & term == "k")) %>%
  humanize() %>%
  ggplot(aes(x = value, y = gain, colour = term)) +
  geom_hline(yintercept = 0.5, size = 0.25, linetype = 2) + 
  geom_point(shape = 21, alpha = 0.5, size = 1) +
  geom_smooth(aes(fill = term), 
              se = F, size = 0.5, method = "glm", 
              method.args = list(family = "binomial"), alpha = 0.1)+
  pub_theme() +
  scale_color_manual(values = colour_scale_values) +  
  scale_fill_manual(values = colour_scale_values) +
  theme(legend.position = "top") +
  labs(colour = "", fill = "", 
       y = "scaled trade-off\nconspecific - heterospecific pollen gain", 
       x = "scaled variable value")
```

@@

This is, the data is best modelled when ignoring the hierarchical nature of the experiment (communities nested in agricultural or restored fragments nested in localities).
Similarly, the relationship between degre and pollen gain does not seem to be species or community dependent.

@@

## Awknowledgements
